---
title: "Accessing the Pinnacle API"
date: "`r Sys.Date()`"
output:
  html_document:
    keep_md: TRUE
    highlight: null
    mathjax: null
    toc: true
    theme: readable
    fold: TRUE
    toc_float:
      collapsed: FALSE
      smooth_scroll: true
---

The [Pinnacle](http://pinnacle.com) manual can be found here :

[http://www.pinnacle.com/en/api/manual](http://www.pinnacle.com/en/api/manual)

***

To use the Pinnacle API you must have an account with [Pinnacle](http://pinnacle.com).

***

Please contact Pinnacle directly at [csd@pinnacle.com](mailto:csd@pinnacle.com) for all account questions. 

***

Pinnacle Terms & Conditions: [http://www.pinnacle.com/en/termsandconditions](http://www.pinnacle.com/en/api/manual)

***

#####The API is not accessible from all IP-Ranges. For example, IP addresses from the UK and the USA are Geo IP blocked.


## The Pinnacle API package

This document covers version >= 2.0 of the package and is
intended to be an introduction to the package, it does **Not** cover all functions.

For a more detailed breakdown, we recommend you explore the functions in the package

The `pinnacle.API` package allows an R user to Access: 

* Pinnacle's API feed, 
* Pregame/Live Odds and Fixtures, 
* Personal Settled/Running Wagers, 
* Balance Information

While also allowing the usage of this data by 

* Placing wagers/parlays. 

Detailed information about what is available is in the Pinnacle API Manual:
https://www.pinnacle.com/en/api/manual


*** 

## Getting the Package

The most recent stable version is on CRAN, and can be installed with:


```{r, echo=TRUE, eval=FALSE}
install.packages('pinnacle.API')
```

Development versions are available via github, and can be installed with the devtools package


```{r, echo=TRUE, eval=FALSE}
install.packages('devtools')
devtools::install_github('marcoblume/pinnacle.API')
```

*** 

## Setup

the package depends on:

 * `data.table` version >= 1.10
 * `openssl`
 * `httr`
 * `jsonlite`
 * `uuid`
 * `purrr`
 * `magrittr`

load and configure it as follows:


```{r, echo=TRUE, eval=FALSE}
 library(pinnacle.API)
```

Please make sure that you understand the terms and conditions.

```{r, echo=TRUE, eval=FALSE}
 AcceptTermsAndConditions()
```

Run the following to store your session credentials:

```{r, echo=TRUE, eval=FALSE}
 SetCredentials()
```

Your credentials are the username and password for logging into www.pinnacle.com.

## Example Usage:

Pull the Sport Data and filter out the leagues that have lines for Soccer available.

```{r, echo=TRUE, eval=FALSE}
# Get Sports
sport_data <- GetSports()
# Get Soccer id
soccer_id <- with(sport_data, id[name == 'Soccer'])
# Get Odds
soccer_data <- showOddsDF(soccer_id)

# Lets select a single record and see what we're looking at
# (transposed for easier reading)
```

A Record Example:
<table>
 <thead>
  <tr>
   <th style="text-align:left;">   </th>
   <th style="text-align:left;"> Data </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> league.id </td>
   <td style="text-align:left;"> 1708 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.events.id </td>
   <td style="text-align:left;"> 702193777 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> sportId </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> last </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.id </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.lineId </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.number </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.cutoff </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.maxSpread </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.maxMoneyline </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.maxTotal </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.maxTeamTotal </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.spreads.hdp </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.spreads.home </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.spreads.away </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.spreads.altLineId </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.totals.points </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.totals.over </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.totals.under </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.totals.altLineId </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.moneyline.home </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.moneyline.away </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.moneyline.draw </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> teamTotal.home.points </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> teamTotal.home.over </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> teamTotal.home.under </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> teamTotal.away.points </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> teamTotal.away.over </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> teamTotal.away.under </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.events.awayScore </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.events.homeScore </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.events.awayRedCards </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.events.homeRedCards </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> sportId.Fixture </td>
   <td style="text-align:left;"> 29 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> last.Fixture </td>
   <td style="text-align:left;"> 102173434 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> league.events.starts </td>
   <td style="text-align:left;"> 2017-04-01T17:00:00Z </td>
  </tr>
  <tr>
   <td style="text-align:left;"> league.events.home </td>
   <td style="text-align:left;"> test1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> league.events.away </td>
   <td style="text-align:left;"> test2 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> league.events.rotNum </td>
   <td style="text-align:left;"> 222222 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> league.events.liveStatus </td>
   <td style="text-align:left;"> 0 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> league.events.status </td>
   <td style="text-align:left;"> H </td>
  </tr>
  <tr>
   <td style="text-align:left;"> league.events.parlayRestriction </td>
   <td style="text-align:left;"> 2 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> sports.id </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> sports.leagues.id </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.events.state </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.events.elapsed </td>
   <td style="text-align:left;"> NA </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.name </td>
   <td style="text-align:left;"> AFC - Champions League </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.homeTeamType </td>
   <td style="text-align:left;"> Team1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.hasOfferings </td>
   <td style="text-align:left;"> FALSE </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.container </td>
   <td style="text-align:left;"> AFC </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.allowRoundRobins </td>
   <td style="text-align:left;"> TRUE </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.leagueSpecialsCount </td>
   <td style="text-align:left;"> 0 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.eventSpecialsCount </td>
   <td style="text-align:left;"> 0 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.eventCount </td>
   <td style="text-align:left;"> 0 </td>
  </tr>
</tbody>
</table>

## Basic Functions

*** 

### Get Client Balance:




```{r, echo=TRUE, eval=FALSE}
GetClientBalance()
```

```
## $availableBalance
## [1] 3896.54
## 
## $outstandingTransactions
## [1] 3522
## 
## $givenCredit
## [1] 1e+05
## 
## $currency
## [1] "USD"
```

*** 

### Get Sports:

```{r, echo=TRUE, eval=FALSE}
Sports <- GetSports()

head(Sports)
```


*** 

### Get Leagues:


```{r, echo=TRUE, eval=FALSE}
BasketBallLeagues <- GetLeaguesByID(4)

# Get first 5 entries Basketball Leagues
head(BasketBallLeagues)
```

*** 

### Get Fixtures:


```{r, echo=TRUE, eval=FALSE}
# Get Basketball Fixtures
BasketballFixtures <- GetFixtures(4)
head(BasketballFixtures)
```

*** 


```{r, echo=TRUE, eval=FALSE}
# Get Live Basketball Fixtures
LiveBasketballFixtures <- GetFixtures(4, islive = 1)
head(LiveBasketballFixtures)
```

*** 

### Get Odds:


```{r, echo=TRUE, eval=FALSE}
# Get Basketball Odds
BasketballOdds <- GetOdds(4)
head(BasketballOdds)
```

*** 


```{r, echo=TRUE, eval=FALSE}
# Get Live Basketball Odds
LiveBasketballOdds <- GetOdds(4, islive = 1)
head(LiveBasketballOdds)
```

*** 

### show Odds DF:

Combines the `GetOdds`, `GetFixtures`, and `GetInrunning` Calls, to get one picture of lines

Column names are slightly different than in the above calls, in that only the last 3 identifiers are kept

##### For example:

`sport.leagues.events.periods.periodNumber`

becomes

`events.periods.periodNumber`

This is done to make the tables easier to work with, but can be overridden (see `?showOddsDF`)

(Default is to show only mainlines, alternate lines are accessible via the `tableFormat` option)


```{r, echo=TRUE, eval=FALSE}
# Get Basketball oddsDF
BasketballOddsDF <- showOddsDF(4)
head(BasketballOddsDF)
```




*** 

### Place Bet

Once we have our odds information, we can use this to make a bet, or string of bets

for the following example, we will place a bet of $0.01 
(Below the minimum bet amount) on the favorite `MONEYLINE`


```{r, echo=TRUE, eval=FALSE}
BasketballOddsDF <- showOddsDF(4,tableFormat = 'mainlines')

```

Record example (filtered to only the interesting fields):

<table>
 <thead>
  <tr>
   <th style="text-align:left;">   </th>
   <th style="text-align:right;"> Data </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> sportId </td>
   <td style="text-align:right;"> 4 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> leagues.events.id </td>
   <td style="text-align:right;"> 704584684 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.number </td>
   <td style="text-align:right;"> 0 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.lineId </td>
   <td style="text-align:right;"> 379913314 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> events.periods.maxMoneyline </td>
   <td style="text-align:right;"> 250 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.moneyline.home </td>
   <td style="text-align:right;"> -477 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> periods.moneyline.away </td>
   <td style="text-align:right;"> 353 </td>
  </tr>
</tbody>
</table>

*** 

Now we can use those details to fill out the PlaceBet arguments


```{r, echo=TRUE, eval=FALSE}
PlaceBet(
    stake = 0.01, 
    sportId = 4,
    eventId = 704584684,
    periodNumber = 0,
    lineId = 379913314,
    betType = 'MONEYLINE',
    team = 'TEAM1'
)
```

Here, our stake is below the minimum amount, as we can see in the error message that is returned

List of 5:

 - status               : chr "PROCESSED_WITH_ERROR"
 - errorCode            : chr "BELOW_MIN_BET_AMOUNT"
 - betId                : NULL
 - uniqueRequestId      : chr "b9d95cf0-54bf-47ee-bad5-4a6dc557da7a"
 - betterLineWasAccepted: logi FALSE

 
 
 If we do it for a larger amount:
 
```{r, echo=TRUE, eval=FALSE}
PlaceBet(
    stake = 500, 
    sportId = 4,
    eventId = 704584684,
    periodNumber = 0,
    lineId = 379913314,
    betType = 'MONEYLINE',
    team = 'TEAM1'
)
```

List of 6:

 - status               : chr "ACCEPTED"
 - errorCode            : NULL
 - betId                : int 706865959
 - uniqueRequestId      : chr "5acf90ff-bbde-4449-af28-b0db7534e249"
 - betterLineWasAccepted: logi FALSE
 - price                : num -477